Constructing hierarchical time series through clustering: \\Is there an optimal way for forecasting?

### 2024-09-03 manuscript/figures/aggcluster_random.tex
update

    \node(A1)[draw, circle, minimum size=0.2cm]{};
    \node(B1)[draw, circle, minimum size=0.2cm, below left=0.5cm of A1]{};

    \node(D1)[draw, circle, minimum size=0.2cm, below left=0.5cm of B1]{};
    \node(F1)[draw, circle, minimum size=0.2cm, below left=0.5cm of D1]{1};
    \node(G1)[draw, circle, minimum size=0.2cm, below right=0.5cm of D1]{2};
    \node(E1)[draw, circle, minimum size=0.2cm, right=0.8727922cm of G1]{3};
    \node(C1)[draw, circle, minimum size=0.2cm, right=0.8727922cm of E1]{4};

    \draw (A1) -- (B1) -- (D1) -- (F1);
    \draw (D1) -- (G1);
    \draw (B1) -- (E1);
    \draw (A1) -- (C1);

    \node(A)[draw, circle, minimum size=0.2cm, right=5cm of A1]{};
    \node(B)[draw, circle, minimum size=0.2cm, below left=0.5cm of A]{};

    \node(D)[draw, circle, minimum size=0.2cm, below left=0.5cm of B]{};
    \node(F)[draw, circle, minimum size=0.2cm, below left=0.5cm of D]{4};
    \node(G)[draw, circle, minimum size=0.2cm, below right=0.5cm of D]{3};
    \node(E)[draw, circle, minimum size=0.2cm, right=0.8727922cm of G]{1};
    \node(C)[draw, circle, minimum size=0.2cm, right=0.8727922cm of E]{2};

    \draw (A) -- (B) -- (D) -- (F);
    \draw (D) -- (G);
    \draw (B) -- (E);
    \draw (A) -- (C);

>>>>

    \node(B1)[draw, circle, minimum size=0.2cm]{};
    \node(A1)[draw, circle, minimum size=0.2cm, above right=0.3cm and 1.2cm of B1]{};
    \node(F1)[draw, circle, minimum size=0.2cm, below left=0.55cm and 0.5cm of B1]{1};
    \node(H1)[draw, circle, minimum size=0.2cm, below right=0.55cm and 0.5cm of B1]{2};

    \node(E1)[draw, circle, minimum size=0.2cm, below right=0.3cm and 1.2cm of A1]{};
    \node(I1)[draw, circle, minimum size=0.2cm, below left=0.55cm and 0.5cm of E1]{3};
    \node(G1)[draw, circle, minimum size=0.2cm, below=0.4cm of E1]{4};
    \node(K1)[draw, circle, minimum size=0.2cm, below right=0.55cm and 0.5cm of E1]{5};

    \draw (A1) -- (B1) -- (F1);
    \draw (H1) -- (B1);
    \draw (A1) -- (E1) -- (G1);
    \draw (K1) -- (E1) -- (I1);

    \node(B)[draw, circle, minimum size=0.2cm, right=6cm of B1]{};
    \node(A)[draw, circle, minimum size=0.2cm, above right=0.3cm and 1.2cm of B]{};
    \node(F)[draw, circle, minimum size=0.2cm, below left=0.55cm and 0.5cm of B]{2};

    \node(H)[draw, circle, minimum size=0.2cm, below right=0.55cm and 0.5cm of B]{4};

    \node(E)[draw, circle, minimum size=0.2cm, below right=0.3cm and 1.2cm of A]{};
    \node(I)[draw, circle, minimum size=0.2cm, below left=0.55cm and 0.5cm of E]{1};
    \node(G)[draw, circle, minimum size=0.2cm, below=0.4cm of E]{5};
    \node(K)[draw, circle, minimum size=0.2cm, below right=0.55cm and 0.5cm of E]{3};

    \draw (A) -- (B) -- (F);
    \draw (H) -- (B);
    \draw (A) -- (E) -- (G);
    \draw (K) -- (E) -- (I);

### 2024-09-03 manuscript/manuscript.tex
update

% \usepackage{natbib}
\usepackage{amsfonts,amsmath,bbm,bm,xcolor,booktabs,hyperref,amsthm}
\usepackage{geometry}
\usepackage{todonotes}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{subfig}
\geometry{a4paper,scale=0.8}
\usepackage{setspace}
\setstretch{1.5}
\let\code=\texttt
\let\proglang=\textsf
\setcounter{MaxMatrixCols}{20}
\usepackage{enumitem}

@@

  \author[label1]{Bohan Zhang\corref{cor1}}
  \address[label1]{School of Economics and Management, Beihang University, Beijing, China}
  \ead{zhangbohan@buaa.edu.cn}
  \cortext[cor1]{Corresponding author.}
  \author[label2]{Anastasios Panagiotelis}
  \address[label2]{The University of Sydney Business School, NSW 2006, Australia}
  \author[label3]{Han Li}
  \address[label3]{Department of Economics, The University of Melbourne, VIC 3010, Australia}

@@

    %the dynamics between ``grouping'' and ``structure'', which lead to an improved understanding of forecast reconciliation.\\

@@

  \begin{keyword}
  Forecast reconciliation \sep
  Hierarchical time series \sep
  Clustering \sep
  Hierarchy construction \sep
  Forecast combination
  \end{keyword}

@@

The rest of the paper is organized as follows. Section~\ref{sec:methodology} describes the trace minimization reconciliation methods employed and the clustering-based hierarchical time series augmentation techniques considered. Section~\ref{sec:cluster} first introduces the two datasets used, and then investigates RQ1, in particular the performance of cluster hierarchy compared to natural hierarchy and two-level hierarchy. Section~\ref{sec:permutation} introduces the novel permutation approach, followed by the investigation of RQ2 via evaluating the performance of natural hierarchy and the best performing cluster hierarchy compared to their respective random twins. To avoid the concern that clusters found in the empirical datasets are spurious, a simulation study is considered in Section~\ref{sec:simulation}. Section~\ref{sec:combination} covers the forecast combination approach raised in RQ3. Section~\ref{sec:conclusion} concludes this paper with discussions on the findings and outlines future research directions. 
Data and code for reproducing the results in this paper are available at \url{https://github.com/AngelPone/project_hierarchy}.

@@

A potential shortcoming to using the time series or forecast error as a representation is their high dimensionality, which is equal to the sample size of the training data. To address this concern, low dimension summaries of ``features'' can be considered. Features have been used in the context
%Features, widely employed in capturing time series characteristics, play a pivotal role in various time series applications, including 
time series clustering by \cite{tianoFeatTSFeaturebasedTime2021}, and for forecasting by \cite{wangUncertaintyEstimationFeaturebased2022} and \cite{ liFeaturebasedIntermittentDemand2023}. 
We consider features of both the raw time series and the in-sample forecast error as representations. After filtering out the features that are constant across all series, we select $56$ features.\footnote{The list and descriptions of features are available in the online GitHub repository.} These time series features are calculated by the \code{tsfeatures} (\citealp{tsfeatures}) package in R. %have been applied in several feature-based forecasting studies, \textit{e.g.}, \cite{montero-mansoFFORMAFeaturebasedForecast2020}.
To the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the context of forecast reconciliation.
%\sout{These representations allow us to gain insights into the diverse aspects of hierarchical time series data}.

@@

@@

%\section*{Acknowledgements}

%Bohan Zhang is supported by the international joint doctoral education fund of Beihang University.

\begingroup
\setstretch{1.15}
\bibliographystyle{agsm}
\bibliography{references.bib}
\endgroup

>>>>

% \usepackage{natbib}
\usepackage{amsfonts,amsmath,bbm,bm,xcolor,booktabs,hyperref,amsthm}
\usepackage{geometry}
\usepackage{todonotes}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{subfig}
\geometry{a4paper,scale=0.8}
\usepackage{setspace}
\setstretch{1.5}
\let\code=\texttt
\let\proglang=\textsf
\setcounter{MaxMatrixCols}{20}
\usepackage{enumitem}
% \usepackage[pagewise]{lineno}

@@

%   \author[label1]{Bohan Zhang\corref{cor1}}
%   \address[label1]{School of Economics and Management, Beihang University, Beijing, China}
%   \ead{zhangbohan@buaa.edu.cn}
%   \cortext[cor1]{Corresponding author.}
%   \author[label2]{Anastasios Panagiotelis}
%   \address[label2]{The University of Sydney Business School, NSW 2006, Australia}
%   \author[label3]{Han Li}
%   \address[label3]{Department of Economics, The University of Melbourne, VIC 3010, Australia}

@@

@@

  \begin{keyword}
  Forecast reconciliation \sep
  Clustering \sep
  Hierarchy construction \sep
  Forecast combination \sep
  Mortality \sep
  Tourism flows
  \end{keyword}

@@

The rest of the paper is organized as follows. Section~\ref{sec:methodology} describes the trace minimization reconciliation methods employed and the clustering-based hierarchical time series augmentation techniques considered. Section~\ref{sec:cluster} first introduces the two datasets used, and then investigates RQ1, in particular the performance of cluster hierarchy compared to natural hierarchy and two-level hierarchy. Section~\ref{sec:permutation} introduces the novel permutation approach, followed by the investigation of RQ2 via evaluating the performance of natural hierarchy and the best performing cluster hierarchy compared to their respective random twins. To avoid the concern that clusters found in the empirical datasets are spurious, a simulation study is considered in Section~\ref{sec:simulation}. Section~\ref{sec:combination} covers the forecast combination approach raised in RQ3. Section~\ref{sec:conclusion} concludes this paper with discussions on the findings and outlines future research directions. 
% Data and code for reproducing the results in this paper are available at \url{https://github.com/AngelPone/project_hierarchy}.

@@

A potential shortcoming to using the time series or forecast error as a representation is their high dimensionality, which is equal to the sample size of the training data. To address this concern, low dimension summaries of ``features'' can be considered. Features have been used in the context
%Features, widely employed in capturing time series characteristics, play a pivotal role in various time series applications, including 
time series clustering by \cite{tianoFeatTSFeaturebasedTime2021}, and for forecasting by \cite{wangUncertaintyEstimationFeaturebased2022} and \cite{ liFeaturebasedIntermittentDemand2023}. 
We consider features of both the raw time series and the in-sample forecast error as representations. After filtering out the features that are constant across all series, we select $56$ features calculated by the \code{tsfeatures} (\citealp{tsfeatures}) package in R. %have been applied in several feature-based forecasting studies, \textit{e.g.}, \cite{montero-mansoFFORMAFeaturebasedForecast2020}.
To the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the context of forecast reconciliation.
%\sout{These representations allow us to gain insights into the diverse aspects of hierarchical time series data}.

@@

% \section*{Acknowledgements}

% Bohan Zhang is supported by the international joint doctoral education fund of Beihang University. Han Li is supported by the Australian Research Council Discovery Projects funding scheme (DP220100090)

@@

% \nolinenumbers
\begingroup
\setstretch{1.15}
\bibliographystyle{agsm}
\bibliography{references.bib}
\endgroup
